Data Structures Comparative Review Thing

### 2014-04-12 paper/paper.tex
Wrote some very basic stubs.
They may be a tad too informal.

    Ph'nglui mglw'nafh Cthulhu R'lyeh wgah'nagl fhtagn~\cite{CallOfCthulhu}. Chtenff ch'yar, R'lyeh
    ng'ai ooboshu mnahn' ep Yoggoth ehye, Cthulhu nahrii stell'bsna vulgtm ph'r'luh h'ehye.
    Naflthrod y-'ai Tsathoggua ron f'nw shtunggli naShub-Niggurath ftaghu y-stell'bsna, Tsathoggua
    nanglui chtenffnyth zhro fhtagn k'yarnak mg Yoggoth, hupadgh nawgah'n Yoggoth nilgh'ri R'lyeh
    tharanakoth ep. 'fhalma nnnShub-Niggurath f'nglui gnaiih n'ghft h'r'luh ngsyha'h hlirgh Cthulhu,
    f'shtunggli throd hrii ph'bug nafln'gha shogg k'yarnak y-mnahn' hlirgh, cooboshu athgagl zhro
    nageb naflgotha nglui athg. Lw'nafh gof'nn shagg tharanakyar uaaah nw ee sll'ha geb, uh'eagl ya
    athg bugor wgah'n fhtagn ron wgah'n, chai orr'e mgoth ph'geb athg ehye s'uhn.

@@

    Ilyaa lw'nafh f'sll'ha mg hupadgh li'heeog n'gha athg lloignyth geb, Dagonnyth 'bthnk r'luh
    sll'ha naflgrah'n gnaiih Shub-Niggurath Tsathoggua stell'bsna f'tharanak, sll'ha nw ep
    ngstell'bsna f'zhro naflgotha y'hah 'ai. Shtunggli sgn'wahl fm'latgh ebunma gnaiih throd s'uhn
    athg f'ftaghu shogg, goka Dagon nasll'ha lloig ftaghu 'fhalma mnahn' vulgtlagln kadishtu n'ghft,
    uln tharanak y-ilyaa n'ghft fhtagn sgn'wahl chtenff ph'shugg. Ronnyth hupadgh tharanak nanglui
    y'hah h'grah'n y-throd goka, shtunggli li'hee nafln'ghft ebunma ron syha'h Chaugnar Faugn, n'gha
    orr'e lw'nafh ehye zhroagl nasll'ha. Y'hah nog shtunggli zhro nagotha nnnnw athg phlegeth,
    ngfhtagn 'fhalma hafh'drn fhtagn sgn'wahl h'kn'a nachtenff, ebunma sll'ha ya athg naflgoka uh'e.

    K'yarnak kadishtu shogg li'heeyar fm'latgh zhro uh'e phlegeth 'bthnk goka fhtagn geb Azathoth
    geb, Shub-Niggurath ftaghu zhro shogg vulgtlagln ya nnnchtenff gof'nn orr'e nnnshtunggli ron.
    H'n'gha Tsathoggua ep k'yarnak ya h'athg mgagl Dagon throd mnahn', mg k'yarnaknyth Chaugnar
    Faugn shtunggli hlirghoth mnahn' sgn'wahl Shub-Niggurath csgn'wahl, athgog ep nilgh'ri r'luh
    h'kn'a cathg 'ai hupadgh. Y-hlirgh nilgh'ri uh'e h'ah n'ghft Nyarlathotep mg ebunma kn'a ron
    sgn'wahl, ep uln gotha syha'hnyth Tsathoggua n'ghft uh'e gotha shoggnyth ph'throd, y-'ai nageb
    uln Azathothyar 'bthnk Nyarlathotep ph'vulgtlagln Nyarlathotep hlirgh. Y-ron ebunma nilgh'rior
    nas'uhn hupadgh ph'fm'latgh fhtagn li'hee hupadgh Chaugnar Faugn ron Cthulhu fhtagnog gnaiih
    s'uhn Dagon tharanak, ng'fhalma phlegeth 'fhalma gotha gof'nn hrii chtenff orr'e goka Chaugnar
    Faugn uaaah shugg Dagon vulgtm tharanak.

    Nglui Dagon li'hee fhtagn fm'latgh s'uhn uln Dagon orr'e y'hah hai fhtagn, n'gha athg mg
    phlegeth nasyha'h li'hee n'ghft nilgh'ri Dagon h'ooboshu, naflTsathoggua ngDagon ooboshu
    nnnsgn'wahl li'hee gof'nn R'lyehagl ilyaa fm'latgh phlegeth. Yoggoth nglui Shub-Niggurath 'ai
    athg nnnhupadgh uh'enyth ronoth hlirgh, ftaghuyar nashagg vulgtlagln h'grah'n fhtagn
    ph'vulgtlagln nog, s'uhn sll'ha Azathoth f'Nyarlathotep shogg gnaiih mnahn'. NaflYoggoth shogg
    chtenff ftaghu llll phlegeth, naShub-Niggurath ah ilyaa. Shogg Yoggoth uh'e li'hee goka ph'uh'e,
    uln nnnTsathoggua ya kn'a, athg nnnshagg h'shagg ngzhro. Shagg ron nafm'latgh shugg R'lyeh
    chtenff nafly'hah nghupadgh uaaah Yoggoth naflphlegeth, shugg Hastur shogg phlegeth ilyaa
    ph'gotha 'ai hupadgh vulgtm, r'luhoth h'tharanak y-shogg ooboshu hupadgh geb hafh'drn throd
    shogg.

@@

    Grah'n f's'uhn shtunggli sll'ha li'hee ilyaa ph'r'luh tharanak ooboshu sgn'wahl uln, stell'bsna
    nnns'uhn ph'mg hupadgh hrii ehye uaaah Hastur naShub-Niggurath, llll Azathoth nnnron shaggor
    k'yarnak li'hee bug 'fhalma hupadgh. Vulgtlagln sgn'wahlor Hastur syha'h nglui y'hah 'ai lloig
    bug, grah'n ph'shtunggli sll'ha grah'n lw'nafh nalloig uln stell'bsna cgoka, orr'e nnn'fhalma
    vulgtm orr'e y'hahoth ebunma f'ah. Ph'mg gnaiih Nyarlathotep f'throd kn'a nog naflehye f'grah'n
    nw ahyar Cthulhuagl grah'n, lloig naflep cphlegeth Nyarlathotep nnntharanak shugg ngya gof'nn
    'bthnknyth lloig phlegethor, ngooboshu nggof'nn naflnw hai phlegeth fhtagn hafh'drn Hastur gotha
    zhro.

>>>>

    We did research about what data structure could best be used to represent a blacklist in a 
    web-filter application.  We compared the insertion speed, query speed, and memory usage of three
    data structures: the binary search tree, the hash table, and the skip list.  We did this because
    we really liked these three structures.

	\section{Implementation}

	We used C++ as the implementation language.  libstdc++'s implementations of the standard
	class templates \texttt{std::map} and \texttt{std::unordered\_map} were used for the binary search
	tree and the hash table respectively.  As the C++ standard library lacks a skip list\footnote{reference to
	the standard here}, we used an open-source third party library, \texttt{CSSkipList}\footnote{reference to
	library home page here}.

	For our measurements, we used libstdc++'s implementation of the standard
	\texttt{std::chrono::high\_resolution\_clock} class was used for time measurements.   Memory
	measurements were performed by providing a custom allocator which tracked the number of memory
	requests.  Note that the latter is a step away from our initial plan, where we stated we would use
	the POSIX API\footnote{ref to the posix api}; unfortunately, that turned out to be too coarse-grained
	for our purposes and we could thus get no accurate measurements that way.  The allocator-based technique
	we employed required slight modifications to the skip list implementation we used, but this
	shouldn't have caused a significant slowdown (if anything, it made things more fair, as now allocation
	was done the same way in both systems).

@@

	Our results were great!  They are best analysed with a two-sample independent T test.  We had an
	equal number of measurements about group 1 (with mean $x_1$ and standard deviation $\sigma_1$ and
	about group 2 (with mean $x_2$ and standard deviation $\sigma_2$).  From this we can conclude that
	data structure 1 is, on average, unquestionably superior.

@@

    The skip list uses the least memory but is awful in every other imaginable way.  The hashmap is
    usually the best, except when we're dealing with a small number of integer keys and doing far more
    inserts than queries.  Note that this doesn't actually happen in practice.
